\documentclass{amsart}
\usepackage{multicol}
\usepackage{kmath,kerkis}
\usepackage{multirow}
\usepackage{fancyvrb}
\usepackage{xcolor}
\usepackage{dirtree}

\newcommand\code[1]{{\bfseries\texttt{#1}}}
\newcommand\ximera{\textsl{Ximera}}
\newcommand\home{$\boldsymbol\sim$}


\fvset{commandchars=+(),formatcom=\color{blue!50!black}}

\begin{document}
\title{\ximera\: Markup in Practice}
\maketitle

\textbf{WARNING} This document is currently under development. 


\tableofcontents

The goal of the \ximera\ Project is to allow authors to write online
interactive content though \LaTeX\ documents.


\section{Philosophy}

Since Ximera is built on \LaTeX\ source, we want to use \LaTeX\ as a
method of validating the code authors write. Hence, if you want to
write a Ximera online activity, the first step is constructing
\LaTeX\ documents. Once you have the \LaTeX\ documents, and you have
checked them for typos, accuracy, etc, the fact that they compile
should be reasonable evidence that they will display correctly in
\ximera.


\section{Setup}

The directory \code{ximeraLatex} contains example files and
\code{ximera.cls}. To get started, you need to put \code{ximeraLatex}
someplace where your installation of \LaTeX\ will find it. This
dependes on your system, but we can give some advice:

\subsection{For Linux}

Create the directory structure \code{\home/texmf/tex/latex/} and place
\code{ximeraLatex} in \code{\home/texmf/tex/latex/}.

\dirtree{%
.1 \home\DTcomment{Your home directory}.
.2 texmf.
.3 tex.
.4 latex.
.5 ximeraLatex.
}


\subsection{For Mac}

Create the directory structure \code{\home/Library/texmf/tex/latex/} and place
\code{ximeraLatex} in \code{\home/Library/texmf/tex/latex/}.

\dirtree{%
.1 \home\DTcomment{Your home directory}.
.2 Library.
.3 texmf.
.4 tex.
.5 latex.
.6 ximeraLatex.
}

\subsection{For Windows (MiKTeX)}


Create the directory structure \code{C:\textbackslash
  localtexmf\textbackslash tex\textbackslash latex\textbackslash} and
place \code{ximeraLatex} in \code{C:\textbackslash localtexmf\textbackslash tex\textbackslash latex\textbackslash}.

\dirtree{%
.1 C:.
.2 localtexmf.
.3 tex.
.4 latex.
.5 ximeraLatex.
}
For MiKteX to notice this directory, go to:
\begin{enumerate}
\item Start $\rightarrow$ All programs $\rightarrow$ MiKTeX Folder $\rightarrow$ Maintenance (Admin) Folder $\rightarrow$ Settings (Admin).
\item Now select the tab ``Roots.''
\item Click ``Add'' because you are going to add a path.
\item Find \code{C:\textbackslash localtexmf\textbackslash} and click
  ``OK.''
\item Click "apply" "OK" and then you are ready to go.
\end{enumerate}
This will allow all of your documents to find \code{ximera.cls}. Note,
it is important that none of the directories containing ximeraLatex
have spaces in their names.

\subsection{Test your system}

At this point we think that
\code{ximeraLatex/firstExample/firstExample.tex},
\code{ximeraLatex/secondExample/secondExample.tex}, and
\code{ximeraLatex/exampleActivityCollection.tex} should compile.  If
you are running windows, then it may be the case that you need to make
copies of these files---and compile them elsewhere.

\section{Writing a new activity}

Now let's write a new activity. The basic structure of the document is:

\begin{Verbatim}
  \documentclass{ximera}
  \input{preamble.tex}
  \title{New activity}
  \begin{document}
  \begin{abstract}
    An attempt to write a new activity.
  \end{abstract}
  \maketitle
  \end{document}
\end{Verbatim}

Note, the \code{abstract} needs to be short. We suggest a single
sentence.

Here the file \code{preamble.tex} contains all of your user-defined
commands. Note, if environments are defined here, they probably will
not work in \ximera. If you have a need for an environment that is not
supplied in \code{ximera.cls}, then you should contact us at
\code{ximera@math.osu.edu}.

To help navigate the collection of activities, authors should try to
include learning prerequisites, and learning outcomes.  Each
prerequisite and outcome should be without spaces, and every attempt
should be made to use already available tags for the prerequisites and
outcomes needed/delivered by this activity.


\begin{Verbatim}
  \documentclass{ximera}
  \input{preamble.tex}
  +color(red)\prerequisites{prereq1} % doesn't work!
  +color(red)\prerequisites{prereq2} % doesn't work!
  +color(red)\outcomes{outcome1}
  +color(red)\outcomes{outcome2}
  \title{New activity}
  \begin{document}
  \begin{abstract}
    An attempt to write a new activity.
  \end{abstract}
  \maketitle
  \end{document}
\end{Verbatim}



\section{Writing basic questions}


The \ximera\ Project offers four basic problem-like environments:
\code{exercise}, \code{question}, \code{exploration}, and
\code{hint}. From the interactive viewpoint, each of these
environments does basically the same thing, providing a question for
the student.

The \code{exercise} environment is for checking computational or rote
performance:

\begin{Verbatim}
  +color(red)\begin{exercise}
    An exercise.
  +color(red)\end{exercise}
\end{Verbatim}

The \code{question} environment is for a more challenging problem.

\begin{Verbatim}
  +color(red)\begin{question}
    A question.
  +color(red)\end{question}
\end{Verbatim}

The \code{exploration} environment is for more open-ended problems. 

\begin{Verbatim}
  +color(red)\begin{exploration}
    An exploration.
  +color(red)\end{exploration}
\end{Verbatim}

The \code{hint} is a sub-question environment that will help with
solving the main question.

Each of these environments (except for hint) can have space after it in via an optional documentclass argument \code{space}.


\begin{Verbatim}
  \documentclass+color(red)[space]+color(blue!50!black){ximera}
  ...
  \begin{exercise}
    An exercise followed by 2 inches of space.
  \end{exercise}

  \begin{exercise}+color(red)[5in]
    An exercise followed by 5 inches of space.
  \end{exercise}

\end{Verbatim}

\section{Adding solutions and answer fields}


As coded above, none of the problem-like environments have answers,
they are simply displayed questions.  For a problem-like environment to
have a solution, we must add a \code{solution} environment.


\begin{Verbatim}
  \begin{question}
    A question.
    +color(red)\begin{solution}
      A solution. 
    +color(red)\end{solution}
  \end{question}
\end{Verbatim}

However, as it stands, the student will be presented with a problem,
and then be able to ``click'' to see the solution. To have an answer
field we to add the \code{answer}. Note, if the answer is a math expression, then the \$ \dots \$ should be inside the answer. 

\begin{Verbatim}
  \begin{question}
    A question.
    \begin{solution}
      A solution. 
      +color(red)\answer{The answer}.
    \end{solution}
  \end{question}
\end{Verbatim}

The default type for an answer is a mathematical expression---hence the argument should be inline math-mode:
\begin{Verbatim}
  \begin{question}
    A question.
    \begin{solution}
      A solution. 
      +color(red)\answer{$6$}.
    \end{solution}
  \end{question}
\end{Verbatim}

However, there are other choices: \code{free-response}, \code{image},
and \code{multiple-choice}. The option \code{free-response} provides a
text field that is ungraded. The option \code{image} allows the
student to upload an image as the solution.

For multiple-choice questions, authors should use the
\code{multiple-choice} environment to list the solutions. This has an
optional argument to display fewer than the total number of
options. No \code{answer} should be given with multiple-choice, as
this information is encoded with the choices. However, a solution
should be given, and this would include things that would aid the
online student, as well as any \code{hints}, see below.

\begin{Verbatim}
  \begin{question}
    A multiple choice question.
    \begin{solution}
    \begin{multiple-choice}[3]
      \choice[correct]{Choice a.}
      \choice{Choice b.}
      \choice[correct]{Choice c.}
      \choice{Choice d.}
    \end{multiple-choice}
       Select the best answer above. 
    \end{solution}
  \end{question}
\end{Verbatim}
Note, the \code{multiple-choice} list needs to go inside the
\code{solution}.

\section{Questions with multiple-parts and hints}

To add questions with multiple parts, simply add more answers to the
solution environment.

\begin{Verbatim}
  \begin{question}
    A question. 
    +color(red)\begin{solution}
      First solution. 
      \answer{First answer}.
    +color(red)\end{solution}
    A follow-up question.
    +color(red)\begin{solution}
      Second solution. 
      \answer{Second answer}.
    +color(red)\end{solution}
  \end{question}
\end{Verbatim}



To add hints to the question, add a \code{hint} within the
\code{solution} environment.



\begin{Verbatim}
  \begin{question}
    A question. 
    \begin{solution}
      +color(red)\begin{hint}
        A hint.
      +color(red)\end{hint}
      A solution. 
      \answer{First answer}.
    \end{solution}
  \end{question}
\end{Verbatim}


Or with a multiple-choice question:

\begin{Verbatim}
  \begin{question}
    A question.
    \begin{solution}
    \begin{multiple-choice}[3]
      \choice[correct]{Choice a.}
      \choice{Choice b.}
      \choice[correct]{Choice c.}
      \choice{Choice d.}
    \end{multiple-choice}
      Select the best answer above. 
      +color(red)\begin{hint}
        A hint.
        +color(red)\end{hint}
    \end{solution}
  \end{question}

To make the hints more Socratic, they themselves can be questions
with solutions with/or without answer fields:

\begin{Verbatim}
  \begin{question}
    A question. 
    \begin{solution}
      +color(red)\begin{hint}
        A hint.
        +color(red)\begin{solution}
        The solution to the question asked by the hint.
        +color(red)\end{solution}
      +color(red)\end{hint}
      +color(red)\begin{hint}
        Another hint.
        +color(red)\begin{solution}
        \answer{An answer to the hint.}
        This time the hint was a question with an answer field.
        +color(red)\end{solution}
      +color(red)\end{hint}
      A solution. 
      \answer{An answer}.
    \end{solution}
  \end{question}
\end{Verbatim}



\section{Presenting one question of a variation of questions}

To allow the student to master a concept, it is often useful to have a
variation of questions that are all presented as a single question in the
online experience. To do this, use the \code{shuffle} command.


\begin{Verbatim}
  +color(red)\begin{shuffle}
    \begin{question}
      A variation of a question, solution etc.
    \end{question}
    
    \begin{question}
      Another variation of a question, solution etc.
    \end{question}
  +color(red)\end{shuffle}
\end{Verbatim}

By default \code{shuffle} initially presents a variation of the
problem at random for the student to solve with the option of
repeating the question, though due to the randomization, the student
will probably be asked to solve a different variation of the
question. As student data is collected, the presentation goes from
truly random to a more adaptive approach, presenting easier or harder
questions based on the student's performance. The highest score
achieved on any of the variations of the question is recorded as the
students performance. There are several options for \code{shuffle},
\begin{description}
\item[\code{once}] Chooses a problem variation at random and allows
  exactly one attempt to solve the problem.
\item[\code{order}] Presents the problems in the order listed to the
  student, should the student choose to attempt the problem multiple
  times.
\item[\code{mastery}] Presents the problems initially at random and
  encourages the student to attempt the problem multiple times. This
  will change to an adaptive presentation after enough data is
  collected. Here the score is based on the aggregate performance,
  rather than the single highest attempt.
\end{description}


\begin{Verbatim}
  +color(red)\begin{shuffle}[mastery]
    \begin{exercise}
      A variation of an exercise, solution etc.
    \end{exercise}
    
    \begin{exercise}
      Another variation of an exercise, solution etc.
    \end{exercise}
  +color(red)\end{shuffle}
\end{Verbatim}



\section{Adding interactive elements}

To add interactive elements, use the \code{interactive} environment.


\begin{Verbatim}
  +color(red)\begin{interactive}[interactiveContent.js]
    Static content.
  +color(red)\end{interactive}
\end{Verbatim}

\section{Images and videos}

To include an image, TikZ or otherwise, use 
\begin{Verbatim}
  +color(red)\begin{image}
    A TikZ Image
  +color(red)\end{image}
\end{Verbatim}


Links to videos can be added with the \code{youtube} or \code{video}
command. If the video is a YouTube video, it is best to use the
\code{youtube} command.

\begin{Verbatim}
  +color(red)\video{some-video-url}
  +color(red)\youtube{some-video-url}
\end{Verbatim}


%% \section{Building a course}\label{S:Course}




%% \dirtree{%
%% .1 ximeraActivities.
%% .2 course.tex.
%% .2 preamble.tex.
%% .2 ximera.cls\DTcomment{A symbolic link to ximeraLatex/ximera.cls}.
%% .2 firstActivity.
%% .3 ximera.cls\DTcomment{A symbolic link to ximeraLatex/ximera.cls}.
%% .3 firstActivity.tex.
%% .3 firstActivitySource.tex.
%% .2 secondActivity.
%% .3 ximera.cls\DTcomment{A symbolic link to ximeraLatex/ximera.cls}.
%% .3 secondActivity.tex.
%% .3 secondActivitySource.tex.
%% .2 thirdActivity.
%% .3 ximera.cls\DTcomment{A symbolic link to ximeraLatex/ximera.cls}.
%% .3 thirdActivity.tex.
%% .3 thirdActivitySource.tex.
%% }

%% The file \code{course.tex} contains the following code:

%% \begin{Verbatim}
%%   \documentclass{ximera}
%%   \input{preamble.tex}
%%   \begin{document}
%%   \title{The Title of the Course}
%%   \author{The authors}
%%   \maketitle
%%   \tableofcontents
%%   \input{./firstActivity/firstActivitySource.tex}
%%   \input{./secondActivity/secondActivitySource.tex}
%%   \input{./thirdActivity/thirdActivitySource.tex}
%% \end{document}
%% \end{Verbatim}


The document class allows for some optional arguments:
\begin{description}
\item[nohints] Displays all questions with solutions but no hints are shown.
\item[handout] Displays the first of each question in a shuffle environment, without solutions or hints.
\item[space] To be used with the \code{handout} option, provides 2
  inches of blank space below each problem. Note: Each problem
  environment also has an optional argument where the author can
  change the amount of space displayed.
\item[numbers] To be used when producing a compilation of
  activities. 
\end{description}




\end{document}
